---
title: "group_XHS_analysis"
author: "Sophie CDY"
date: "2025-04-15"
output: html_document
---

```{r setup}
library(dplyr)
library(readr)
library(ggplot2)
library(psych)

options(scipen = 999)

usgae_levels <- c(
  "less than 0.5 hour", 
  "0.5-1 hour", 
  "1-2 hours", 
  "more than 2 hours")

likert_levels <- c(
  "Strongly Disagree", 
  "Disagree", 
  "Neither agree nor disagree", 
  "Agree", 
  "Strongly Agree")

group_xhs <- read_csv(
  '../data/XHS_data.csv',
  col_types = cols(
    col_factor(ordered = TRUE, levels = usgae_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels),
    col_factor(ordered = TRUE, levels = likert_levels)
  ))

group_xhs <- group_xhs %>%
  mutate(
    across(
      .cols = c(starts_with('IS'), starts_with('CA'), starts_with('CB')),
      .fns = as.numeric,
      .names = '{.col}_coded'
    )
  )

keys_list <- list(
  IS = c(
    'IS1_coded',
    'IS2_coded',
    'IS3_coded',
    'IS4_coded',
    'IS5_coded'
  ),
  CA = c(
    'CA1_coded',
    'CA2_coded',
    'CA3_coded',
    'CA4_coded'
  ),
  CB = c(
    'CB1_coded',
    'CB2_coded',
    'CB3_coded',
    'CB4_coded',
    'CB5_coded'
  )
)

xhs_scores <-scoreItems(
  keys = keys_list,
  items = group_xhs,
  totals = FALSE,
  missing = TRUE,
  impute = 'none'
)

group_xhs <- cbind(group_xhs, xhs_scores$scores)

```

#Descriptive statistics
```{r visualise-time}
group_xhs %>%
  ggplot(
    aes(x = usage_duration, fill = usage_duration)
  ) +
  geom_bar() +
  scale_fill_brewer(palette = "Spectral") 
```
##三个变量的平均数和方差
sapply(group_xhs[, c("IS", "CA", "CB")], mean, na.rm = TRUE)
sapply(group_xhs[, c("IS", "CA", "CB")], sd, na.rm = TRUE)

# Hypotheses
H1: Information search satisfaction will be positively related to the usage duration of Xiaohongshu.
```{r IS-visualisation}
#IS总分vs使用时长
group_xhs %>%
  ggplot(aes(x = IS, y = usage_duration)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.6) 

ggplot(data = group_xhs, aes(x = IS, y = usage_duration)) +
  geom_boxplot(fill = "lightblue") +
  labs(x = "IS", y = "Usage Duration") +
  theme_minimal()

#IS小分vs使用时长
subvars <- c("IS1_coded", "IS2_coded", "IS3_coded", "IS4_coded", "IS5_coded")
for (subvar in subvars) {
  p <- group_xhs %>%
    ggplot(aes(x = subvar, y = usage_duration)) + 
    geom_boxplot()
  
  print(p)
}

subvars <- c("IS1_coded", "IS2_coded", "IS3_coded", "IS4_coded", "IS5_coded")
for (subvar in subvars) {
  p <- group_xhs %>%
    ggplot(aes(x = subvar, y = usage_duration)) + 
    geom_jitter(width = 0.2, height = 0.1, alpha = 0.3) +
    geom_smooth(method = "lm", se = FALSE)
  
  print(p)
}

```
```{r visualise-IS}
group_xhs %>%
  ggplot(
    aes(x = IS, fill = IS)
  ) +
  geom_bar() +
  scale_fill_brewer(palette = "Spectral") 
```

```{r IS-correlation}
#IS总体vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + IS,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
  
#IS1vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + IS1_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
  
#IS2vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + IS2_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
  
#IS3vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + IS3_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
  
#IS4vs时长 
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + IS4_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )

#IS5vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + IS5_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
```
IS极弱正相关，且没有统计学意义上的显著相关性
IS1存在小到中等程度的正相关，且达到统计显著水平
IS2极弱正相关，且没有统计学意义上的显著相关性
IS3极弱正相关，且没有统计学意义上的显著相关性
IS4极弱正相关，且没有统计学意义上的显著相关性
IS5极弱正相关，且没有统计学意义上的显著相关性

H2: Comment section atmosphere satisfaction will be positively related to the usage duration of Xiaohongshu.
```{r IS-correlation}
#CA总体vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + CA,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
  
#CA1vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + CA1_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
  
#CA2vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + CA2_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
  
#CA3vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + CA3_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
  
#CA4vs时长 
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + CA4_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )

```
CA极弱正相关，且没有统计学意义上的显著相关性
CA1极弱正相关，且没有统计学意义上的显著相关性
CA2极弱正相关，且没有统计学意义上的显著相关性
CA3极弱正相关，且没有统计学意义上的显著相关性
CA4极弱负相关，且没有统计学意义上的显著相关性

H3: Community belonging will be positively related to the usage duration of Xiaohongshu.
```{r IS-correlation}
#CB总体vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + CB,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
  
#CB1vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + CB1_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
  
#CB2vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + CB2_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
  
#CB3vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + CB3_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
  
#CB4vs时长 
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + CB4_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )

#CB5vs时长
  group_xhs %>%
    mutate(
      usage_duration = as.numeric(usage_duration)
    )  %>%
    cor.test(
      ~ usage_duration + CB5_coded,
      data = .,
      method = 'spearman',
      exact = FALSE
    )
```
CB弱正相关,边缘显著
CB1弱正相关，边缘显著
CB2极弱正相关，且没有统计学意义上的显著相关性
CB3弱正相关，且没有统计学意义上的显著相关性
CB4极弱正相关，且没有统计学意义上的显著相关性
CB5极弱正相关，且没有统计学意义上的显著相关性

#草稿
##散点图
ggplot(group_xhs, aes(x = CB, y = as.numeric(usage_duration))) +
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.6) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "CB1", y = "Usage Duration (as numeric)")

##合并组别检验
###dummy variable
group_xhs$usage_group <- ifelse(group_xhs$usage_duration %in% c("less than 0.5 hour", "0.5-1 hour"),"low", "high")
group_xhs$IS1_group <- ifelse(group_xhs$IS1 %in% c("Strongly Disagree", "Disagree", "Neither agree nor disagree"),"low", "high")
table(group_xhs$usage_group)
table(group_xhs$IS1_group)
fisher.test(x = group_xhs$IS1_group, y = group_xhs$usage_group)

###PLS偏最小二乘回归
library(pls)
X <- group_xhs[, c("IS1_coded", "IS2_coded", "IS3_coded", "IS4_coded", "IS5_coded",
                   "CA1_coded", "CA2_coded", "CA3_coded", "CA4_coded",
                   "CB1_coded", "CB2_coded", "CB3_coded", "CB4_coded", "CB5_coded")]
                   
group_xhs$usage_num <- as.numeric(factor(group_xhs$usage_duration, 
                      levels = c("less than 0.5 hour", 
                      "0.5-1 hour", 
                      "1-2 hours",
                      "more than 2 hours")))
y <- group_xhs$usage_num

pls_model <- plsr(y ~ as.matrix(X), scale = TRUE, validation = "CV")
summary(pls_model)
loadings(pls_model) 


